Measurement of total hadronic differential cross sections in the LArIAT experiment

### 2018-04-09 Chapter-1/1-Theory.tex
s

\begin{equation}
U_{PMNS}=\\
\left[ 
\begin{array}{ccc}
c_{12} & s_{12} & 0\\
-s_{12} & c_{12} & 0\\
0 & 0 & 1\\
\end{array}
\right]
\left[ 
\begin{array}{ccc}
c_{13} & 0 &s_{13}e^{-i\delta} \\
0 & 1 & 0\\
-s_{13}e^{-i\delta}& 0 & c_{13}\\
\end{array}
\right]
\left[
\begin{array}{ccc}
1 & 0 & 0\\
0 & c_{23} & s_{23} \\
0& -s_{23} & c_{23} \\
\end{array}
\right]
\left[ 
\begin{array}{ccc}
e^{i\alpha_1} & 0 & 0\\
0& e^{i\alpha_2} & 0\\
0 & 0 & 1\\
\end{array}
\right]
\end{equation}

@@

%%%%%%%%%%
Hints to the existence of at least one additional neutrino, in the form of various anomalies, have been puzzling physicists almost from the beginning of neutrino oscillation searches. 
Originally designed to look for evidence of neutrino oscillation, the Liquid Scintillator Neutrino Detector (LSND) \cite{Athanassopoulos1997} provided a first conflicting result with the Standard Model expectation of only three neutrino flavors. A second conflicting result has also been provided by the MiniBooNE experiment \cite{AGUILARAREVALO200928}.
The  LSND and MiniBooNE $\nu_e$ and $\bar\nu_e$ appearance results, known as the ``LSND and MiniBooNE anomalies" \cite{Aguilar:2001ty, Athanassopoulos:1997pv, Aguilar-Arevalo:2013pmq}, may be interpreted under the assumption of a new neutrino. The additional neutrino needs to be ``sterile", i.e needs not to couple with the electroweak force carriers, in order to be consistent with the measurement of the width of the Z boson~\cite{2006257}.  The new sterile neutrino would mainly be composed of a heavy neutrino $\nu_4$ with mass $m_4$ such that  $m_1, m_2, m_3 \ll m_4$ and  $\Delta m^2= \Delta m^2_{14} \sim [0.1 - 10]$ eV$^2$.
The introduction of sterile neutrinos is an appealing line of thinking, since this renormalizable generalization of the Standard Model has the potential to impact long standing questions in high energy physics and cosmology: light sterile neutrinos are candidates for dark matter particles and there are ideas that the theory could be adjusted to explain the baryon asymmetry of the Universe via leptogenesis \cite{1063-7869-57-5-503}.

%%%%%%%%%%
\begin{enumerate}
\item CP violation in the neutrino sector, and mass ordering and determination of the octant => hidden symmetries and . 
\item Neutrino nature Majorana or Dirac?
\item Neutrino masses?
\end{enumerate}

>>>>

\begin{equation}
U_{PMNS}=\\
\left[ 
\begin{array}{ccc}
c_{12} & s_{12} & 0\\
-s_{12} & c_{12} & 0\\
0 & 0 & 1\\
\end{array}
\right]
\left[ 
\begin{array}{ccc}
c_{13} & 0 &s_{13}e^{-i\delta} \\
0 & 1 & 0\\
-s_{13}e^{-i\delta}& 0 & c_{13}\\
\end{array}
\right]
\left[
\begin{array}{ccc}
1 & 0 & 0\\
0 & c_{23} & s_{23} \\
0& -s_{23} & c_{23} \\
\end{array}
\right]
\left[ 
\begin{array}{ccc}
e^{i\alpha_1} & 0 & 0\\
0& e^{i\alpha_2} & 0\\
0 & 0 & 1\\
\end{array}
\right]
\label{eq:PMNS}
\end{equation}

@@

%%%%%%%%%%
Hints to the existence of at least one additional neutrino, in the form of various anomalies, have been puzzling physicists almost from the beginning of neutrino oscillation searches. 
Originally designed to look for evidence of neutrino oscillation, the Liquid Scintillator Neutrino Detector (LSND) \cite{Athanassopoulos1997} provided a first conflicting result with the Standard Model expectation of only three neutrino flavors. A second conflicting result has also been provided by the MiniBooNE experiment \cite{AGUILARAREVALO200928}.
The  LSND and MiniBooNE $\nu_e$ and $\bar\nu_e$ appearance results, known as the ``LSND and MiniBooNE anomalies" \cite{Aguilar:2001ty, Athanassopoulos:1997pv, Aguilar-Arevalo:2013pmq}, may be interpreted under the assumption of a new right-handed neutrino. The additional neutrino needs to be ``sterile", i.e needs not to couple with the electroweak force carriers, in order to be consistent with the measurement of the width of the Z boson~\cite{2006257}.  The new sterile neutrino would mainly be composed of a heavy neutrino $\nu_4$ with mass $m_4$ such that  $m_1, m_2, m_3 \ll m_4$ and  $\Delta m^2= \Delta m^2_{14} \sim [0.1 - 10]$ eV$^2$.
The introduction of sterile neutrinos is an appealing line of thinking, since this renormalizable generalization of the Standard Model has the potential to impact long standing questions in high energy physics and cosmology: light sterile neutrinos are candidates for dark matter particles and there are ideas that the theory could be adjusted to explain the baryon asymmetry of the Universe via leptogenesis \cite{1063-7869-57-5-503}.

%%%%%%%%%%
The measurement of non-zero value for the oscillation parameter $\theta_{13}$ unleashes the exploration of low-energy CP violation in the neutrino sector. Using the parameterization of the PMNS matrix shown in Equation \ref{eq:PMNS},  the difference in the probability of $\nu_e$ to $\nu_\mu$ oscillation and the probability of $\bar\nu_e$ to $\bar\nu_\mu$ oscillation can be parametrized as follows,
\begin{equation}
P_{\nu_e\rightarrow\nu_\mu} - P_{\bar\nu_e\rightarrow\bar\nu_\mu} = J \cos\Big(\pm\delta - \frac{\Delta_{31} L}{2}\Big) \sin\Big(\frac{\Delta_{21} L}{2}\Big)\sin\Big(\frac{\Delta_{31} L}{2}\Big)
\end{equation}
\textcolor{red}{asymmetry formula}
where. 
  The magnitude of the CP- violating terms in the oscillation depends  directly on the size of the Jarlskog Invariant [56], but it aslo related to the octant and the the mass hiararchy.

Exciting theoretical results tie low-energy CP violation in the neutrino sector directly to the generation of the baryon asymmetry of the Universe at the Grand Unified Theory scale \textcolor{red}{a couple of cit would be nice}. According to theoretical model described in \cite{PASCOLI20071}, for example, leptogenesis can be achieved if $|\sin\theta_{13} \sin \delta| > 0.11$, i.e. $\sin \delta > 0.7$.

\begin{enumerate}

\item CP violation in the neutrino sector, and mass ordering and determination of the octant => hidden symmetries and .

%%%%%%%%%%%%%%%%%%%%%%%%%%

\item Neutrino nature Majorana or Dirac?
\item Neutrino masses?
\end{enumerate}
